On the relation between metacognitive monitoring and domain knowledge

### 2019-12-12 ms.Rmd
WIP toward unskilled and unaware revisited

---
title: "On the relation between metacognitive monitoring and domain knowledge"
shorttitle: "Metacognitive resolution and domain knowledge"

author: 
  - name: "Matti Vuorre"
    affiliation: "1"
    corresponding: yes
    address: "406 Schermerhorn Hall, 1190 Amsterdam Avenue, New York, NY 10027"
    email: "vuorre@psych.columbia.edu"
  - name: "Janet Metcalfe"
    affiliation: "1"

affiliation:
  - id: "1"
    institution: "Columbia University"

authornote: |
  This research was supported, in part, by Institute of Education Science grant (R305A150467) awarded to JM. The authors are solely responsible for the content of this article. The data and code supporting this manuscript are available at https://osf.io/np3cu/.

abstract: |
  Metacognitive resolution refers to people's ability to tell their correct answers apart from incorrect answers, and is theorized an important factor in learning. Resolution---the trial-by-trial association between response accuracy and metacognitive endorsement of that response's accuracy---is a distinct ability from knowledge in the domain of testing, and instead indicates a higher-order self-evaluation. It is therefore important that measures of resolution are independent of domain knowledge. Six multiple-choice mathematics experiments revealed a robust positive correlation between resolution and performance. A simulation study suggested that correct guesses afforded by multiple-choice testing necessarily lead to a correlation between resolution and performance. Finally, an experiment supported this hypothesis: Resolution and performance were positively correlated in multiple-choice, but not in free-response testing. These results suggest that the "unskilled and unaware" effect, whereby poorly performing individuals appear unaware of their lack of ability, may be artifactual in multiple-choice tasks that define "awareness" as metacognitive resolution.

keywords: "metacognition, confidence, measurement, unskilled and unaware"
wordcount: "`r wordcountaddin::word_count()`"

bibliography: "references.bib"

floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: no
mask: no
draft: no

documentclass: "apa6"
classoption: "man"
output: 
  papaja::apa6_pdf:
    keep_tex: false
  papaja::apa6_word:
    default 
---

@@

To successfully improve learning, it is important that people are able to monitor what they know and what they don't know [@BjorkMemoryMetamemoryConsiderations1994; @FlavellMetacognitioncognitivemonitoring1979; @MetcalfeMetacognitiveJudgmentsControl2009; @NelsonMetamemoryTheoreticalFramework1990; @NelsonUtilizationMetacognitiveJudgments1994]. This metacognitive monitoring and knowledge, when accurate, may be used to select appropriate items for further study or to seek assistance to improve comprehension. To paraphrase the oft-quoted adage: If you don't know what you don't know, you can't fix it. It is therefore of paramount importance that people be metacognitively accurate in all fields of study.

The relative accuracy, or *resolution*, of metacognitive judgments measures the extent to which people can discriminate whether they answered (or will answer) a particular question accurately, on an item-by-item basis. A strong positive relation between a participant's ratings about how sure they are that they are, or will be, correct on particular items and their actual correctness on those items indicates good resolution. Broadly, research has focused on two types of metacognitive ratings: Prospective ratings, such as judgments of learning (JOL), feelings of knowing (FOK) or ease of learning judgments (EOL), indicate how likely the participant thinks that a later retrieval or answer will be correct. Retrospective ratings indicate the participant's judgment of the accuracy of a just-provided answer, typically in the form of judgments of confidence. Although these judgments are distinct, for clarity we refer to all as judgments of confidence (in the accuracy of one's answer). Typically, the correspondence between confidence and accuracy is referred to as metacognitive resolution, relative accuracy [@DunloskyMetacognition2009], or sensitivity [@FlemingHowmeasuremetacognition2014].

Another aspect of metacognitive accuracy, sometimes termed calibration, absolute accuracy, bias, or over/underconfidence, concerns the relationship between participants' average level of performance and average metacognitive judgment magnitude [@DunloskyMetacognition2009; @Lichtensteinthosewhoknow1977]. For example, it has been found that individuals with poorer performance in a task tend to overestimate their task abilities, a phenomenon known as the Dunning-Kruger effect [@KrugerUnskilledUnawareIt1999]. Although sometimes also called metacognitive accuracy, calibration is distinct from the topic of this manuscript, metacognitive resolution.

@@

Metacognitive resolution is typically measured with metrics that are asserted to be independent of the participants' performance, skill, or knowledge in the primary task. For example, in a memory task, participants' memory abilities should not impact their metacognitive abilities, and vice versa. In an influential article @Nelsoncomparisoncurrentmeasures1984 recommended the Goodman-Kruskal gamma correlation [@GoodmanMeasuresAssociationCross1954] as a measure of resolution, partly because it is theoretically independent of task performance [see also @GonzalezMeasuringordinalassociation1996]. Other measures of resolution include Pearson's *r* [@NelsonNorms300generalinformation1980], the phi correlation [@KornellTransferMetacognitiveSkills2007], and signal detection theoretic measures [@benjamin2008measurement; @HighamNewimprovedgamma2018]. Although computationally different, these metrics measure the association between response accuracy and metacognitive rating in a way that is usually assumed to quantify metacognitive ability independent of task performance. However, it remains a possibility that metacognitive resolution is empirically related to task performance, with important implications to self-directed study.

@@

How important is metacognitive monitoring---resolution---to learning success? One review of 47 experiments found that not only do learners allocate more time to more difficult items, learners' metacognitive judgments negatively predict the amount of time they allocate for studying that item [@SonMetacognitivecontrolstrategies2000]. These results suggest that people are aware of how well they know and use this metacognitive knowledge to guide learning, leading to the hypothesis that students with greater metacognitive resolution may be better learners: Resolution and task performance should be positively correlated across participants. If true, this finding would further support the proposal that metacognitive monitoring is used to control learning behavior, with a positive impact on learning success [@nelson1994investigate].

@@

In what we call Experiment 1, we collated data from six experiments investigating mathematics learning. There were differences between experiments, such as testing medium (computer or paper) and age (middle school or undergraduate), but our focus here was not to investigate these factors' impact on mathematics performance or metacognition. Rather, we used this large dataset to examine the possible relationship between metacognitive resolution and (mathematics) performance, in a multiple-choice testing context. The common procedure was that participants completed mathematics tests consisting of 4-alternative multiple-choice problems, and rated their confidence in the accuracy of each of their answers.

With respect to resolution in mathematics study, two previous studies which contained a resolution measure have reported conflicting results. @SieglerDevelopmentalindividualdifferences2013, in a study of middle school students' fraction arithmetic skills, reported that students' confidence ratings were on average 0.7 points greater for correct than incorrect answers on a 1-5 scale, suggesting that young learners of mathematics have reasonably accurate metacognitions about their answers' accuracy (though the difference in confidence is small). @SchrawEffectGeneralizedMetacognitive1996 tested university undergraduates on probability problems and had them rate their confidence in their answers. The correlation between confidence and accuracy in that study was not statistically significant (Pearson's *r* = -.03)[^1], indicating that university students' metacognitive resolution (within probability calculations) is not accurate. However, neither study addressed the potential correlation between resolution and mathematics performance, which we investigate here.

@@

## Experiment 1A: Method

@@

### Procedure

@@

## Experiment 1B: Method

@@

## Experiment 1C: Method

@@

## Experiment 1D: Method

@@

## Experiment 1E: Method

@@

## Experiment 1F: Method

@@

In this experiment, participants completed four mathematics tests as part of an online mathematics tutorial. Each test consisted of ten problems, presented alone on the top of the screen, with the answer alternatives below. Participants chose their preferred response by clicking a box next to it. They then clicked "Submit", and proceeded to the next screen, where they rated their confidence in the accuracy of their response by clicking on a visual analog scale. After indicating their degree of confidence, they clicked "Submit" to proceed to the next screen. The following screen allowed the participant to view different types of instructional videos related to the mathematics problems, but these are not analyzed in the current study. The tests were completed in one 90-minute session, on individual computers, in groups of up to four supervised by an experimenter.

@@

```{r math-dtab}
new_names <- tibble(
  key = c("zroc_auc_gamma", "gamma_old", "zroc_da", "phi", "zroc_auc", "trap_auc", "proportion_correct", "mean_rating"),
  Metric = c("Gamma (ROC)", "Gamma (pairs)", "da", "Phi", "AUC (zROC)", "AUC (trap)", "Proportion Correct", "Mean confidence")
)
tab <- math_metrics %>%
  gather(key, value, proportion_correct, zroc_auc_gamma, zroc_da, gamma_old) %>%
  group_by(key, Experiment) %>%
  group_modify(~ data.frame(t(smean.cl.boot(.x$value, B = 1000)))) %>%
  ungroup() %>%
  left_join(new_names) %>%
  right_join(math_subjects) %>%
  mutate_at(vars(Mean, Lower, Upper), ~ format(round(., 2), nsmall = 2)) %>%
  mutate(result = glue("{Mean} [{Lower}, {Upper}]")) %>%
  select(Experiment, N, Metric, result) %>%
  spread(Metric, result) %>%
  select(Experiment, N, `Proportion Correct`, everything())
kable(
  tab, 
  booktabs = TRUE,
  caption = "Measures of mathematics performance and resolution in Experiment 1. Numbers indicate means with 95\\% CIs in square brackets."
  )
```

@@

```{r math-rtab}
tab <- math_metrics %>%
  gather(key, value, zroc_da, zroc_auc_gamma, gamma_old) %>%
  left_join(new_names) %>%
  group_by(Experiment, Metric) %>% 
  group_modify(
    ~tidy(cor.test(.x$value, .x$proportion_correct, method = "kendall"))
  ) %>%
  mutate(p.value = pvalue(p.value)) %>%
  mutate(result = format(round(estimate, 2), nsmall = 2, trim = TRUE)) %>%
  mutate(result = glue("{result} ({p.value})")) %>%
  select(Experiment, Metric, result) %>%
  ungroup() %>%
  pivot_wider(names_from = c(Metric), values_from = result)
kable(
  tab, 
  booktabs = TRUE,
  caption = "Correlation between mathematics performance and three metrics of metacognitive resolution in Experiment 1."
)
```

@@

```{r trivia-dtab}
tmp1 <- trivia_metrics %>% 
  select(
    session, condition, proportion_correct, 
    mean_rating, gamma_old, zroc_da, zroc_auc_gamma
  ) %>% 
  gather(key, value, -session, -condition) %>% 
  spread(condition, value) %>% 
  mutate(difference = `2AFC`-Free) %>% 
  group_by(key) %>% 
  group_modify(~tidy(t.test(.$difference))) %>% 
  # mutate(p.value = pvalue(p.value), parameter = round(parameter, 0)) %>% 
  mutate_if(is.numeric, ~format(round(., 2), nsmall = 2)) %>%
  ungroup() %>% 
  transmute(
    key = key,
    result = glue("{estimate} [{conf.low}, {conf.high}]")
  ) %>% 
  left_join(new_names) %>% 
  select(-key) %>% 
  spread(Metric, result) %>% 
  add_column(condition = "2AFC - Free", .before = 1)
tmp2 <- trivia_metrics %>%
  gather(
    key, 
    value, 
    proportion_correct, mean_rating, gamma_old, zroc_auc_gamma, zroc_da,
  ) %>% 
  group_by(key, condition) %>%
  group_modify(~ data.frame(t(smean.cl.boot(.x$value, B = 1000)))) %>%
  ungroup() %>%
  left_join(new_names) %>%
  mutate_at(vars(Mean, Lower, Upper), ~ format(round(., 2), nsmall = 2)) %>%
  mutate(result = glue("{Mean} [{Lower}, {Upper}]")) %>%
  select(condition, Metric, result) %>%
  spread(Metric, result) %>%
  select(condition, `Proportion Correct`, `Mean confidence`, everything())
bind_rows(tmp2, tmp1) %>% 
  kable(
    booktabs = TRUE,
    caption = "Measures of general information test performance and metacognition in Experiment 2. Numbers indicate means with 95\\% CIs in square brackets."
  ) %>% 
  kable_styling(latex_options = "scale_down")
```

@@

```{r trivia-ctab}
tmp <- trivia_metrics %>%
  gather(key, value, gamma_old, zroc_da, zroc_auc_gamma) %>%
  left_join(new_names) %>%
  group_by(condition, Metric)
tab <- group_modify(
  tmp,
  ~tidy(cor.test(.x$value, .x$proportion_correct, method = "kendall"))
) %>%
  mutate(p.value = pvalue(p.value)) %>%
  mutate(result = format(round(estimate, 2), nsmall = 2, trim = TRUE)) %>%
  mutate(result = glue("{result} ({p.value})")) %>%
  select(condition, Metric, result) %>%
  ungroup() %>%
  pivot_wider(names_from = c(Metric), values_from = result)
kable(
  tab, 
  booktabs = TRUE,
  caption = "Correlation between general information test performance and three metrics of metacognitive resolution in Experiment 2."
  )
```

>>>>

---
title: "On the relation between metacognitive monitoring and domain knowledge"
shorttitle: "Metacognitive resolution and domain knowledge"
author: 
  - name: "Matti Vuorre"
    affiliation: "1"
    corresponding: yes
    address: "406 Schermerhorn Hall, 1190 Amsterdam Avenue, New York, NY 10027"
    email: "vuorre@psych.columbia.edu"
  - name: "Janet Metcalfe"
    affiliation: "1"
affiliation:
  - id: "1"
    institution: "Columbia University"
authornote: |
  This research was supported, in part, by Institute of Education Science grant (R305A150467) awarded to JM. The authors are solely responsible for the content of this article. The data and code supporting this manuscript are available at https://osf.io/np3cu/.
abstract: |
  Are unskilled people less aware of their (lack of) skill than are their more skilled peers? The idea that unskilled people are also unaware (the "Dunning-Kruger effect") is supported by data from many domains, and has largely concerned people's predictions or retrodictions of their performance in a given task. However, we suggest that if "awareness" is operationalized differently, as relative metacognitive accuracy, the apparent correlation between skill and awareness may be artificially induced by common methods of multiple-choice testing. In the metacognitive research tradition, relative accuracy---the trial-by-trial association between response accuracy and metacognitive endorsement of that response's accuracy---is a more specific measure of awareness than is a one-shot retrodiction or prediction of performance; it directly answers the question "how well do you know that you (don't) know". 
  We found a robust positive correlation between resolution and performance in six multiple-choice mathematics experiments, evidencing the "unskilled and unaware" phenomenon. However, when we directly compared multiple-choice to free-response testing in an otherwise identical task, we found that the correlation between skill and awareness disappeared in free-response testing. We then examined the hypothesis that guessing in a multiple choice test would directly lead to an illusory "unskilled and unaware" effect using monte carlo simulation. The results of that simulation strongly suggested that the correlation between skill and awareness observed in multiple choice testing is an artifact due to guessing, and not indicative of decreased awareness in less skilled individuals. We also discuss the implications of these findings to measurement of metacognitive accuracy.

keywords: "metacognition, confidence, measurement, unskilled and unaware"
wordcount: "`r wordcountaddin::word_count()`"
bibliography: "references.bib"
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: no
mask: no
draft: no
documentclass: "apa6"
classoption: "man"
always_allow_html: true
output: 
  papaja::apa6_word:
    default 
  papaja::apa6_pdf:
    keep_tex: false
---

@@

To successfully improve learning, it is important that people are able to monitor what they know and what they don't know [@BjorkMemoryMetamemoryConsiderations1994; @FlavellMetacognitioncognitivemonitoring1979; @MetcalfeMetacognitiveJudgmentsControl2009; @NelsonMetamemoryTheoreticalFramework1990; @NelsonUtilizationMetacognitiveJudgments1994]. This metacognitive monitoring and knowledge, when accurate, may be used to select appropriate items for further study, seek assistance to improve comprehension, or otherwise change behavior when external feedback is not available. To paraphrase the oft-quoted adage: If you don't know what you don't know, you can't fix it. It is therefore of paramount importance that people be metacognitively accurate.

However, it has repeatedly been found, across a wide range of tasks, that people who are less skilled at a given task are also less aware of their performance in the task (the "unskilled and unaware effect", also known as the "Dunning-Kruger effect"; @KrugerUnskilledUnawareIt1999). For example, @KrugerUnskilledUnawareIt1999 (Study 3) had volunteers read sentences that missed parts. For each sentence, their task was to determine whether the sentence was grammatical or not, and if not, which of four different rewordings would make it grammatical. Afterwards, the participants estimated how many items they completed succesfully. The findings indicated a dramatic unskilled and unaware effect: The worst-performing participants grossly overestimated their test scores, whereas better performing participants were more accurate in their self-evaluations. It appears, then, that unskilled individuals may suffer from a metacognitive mismatch by which they tend to dramatically overestimate their skill, which potentially negative implications to learning, adjustment, and behavior.

This popular measure of self-evaluation by which participants predict or retrodict their performance in a task is typically called metacognitive calibration, absolute accuracy, bias, or over/underconfidence [@DunloskyMetacognition2009; @Lichtensteinthosewhoknow1977]. However, in the metacognitive research tradition, another, related but not identical, measure is typically used to measure metacognitive awareness.

The relative accuracy, or *resolution*, of metacognitive judgments measures the extent to which people can discriminate whether they answered (or will answer) a particular question accurately, on an item-by-item basis. Arguable, it is a more suitable operationalization of "awareness" than is calibration, because it indicates an online, in-the-moment, evaluation of one's performance in a task. A strong positive relation between a participant's ratings about how sure they are that they are, or will be, correct on particular items and their actual correctness on those items indicates good resolution. Broadly, research has focused on two types of metacognitive ratings: Prospective ratings, such as judgments of learning (JOL), feelings of knowing (FOK) or ease of learning judgments (EOL), indicate how likely the participant thinks that a later retrieval or answer will be correct. Retrospective ratings indicate the participant's judgment of the accuracy of a just-provided answer, typically in the form of judgments of confidence. Although these judgments are distinct, for clarity we refer to all as judgments of confidence (in the accuracy of one's answer). Typically, the correspondence between confidence and accuracy is referred to as metacognitive resolution, relative accuracy [@DunloskyMetacognition2009], or sensitivity [@FlemingHowmeasuremetacognition2014].

@@

Importantly, the unskilled and unaware phenomenon is typically studied using calibration as a measure of awareness.  However, that metric is known to suffer from various drawbacks that can lead to artificial correlations between skill and awareness [@FeldEstimatingrelationshipskill2017; @KrajcAreunskilledreally2008; @McIntoshWiseClarifyingrole2019]. A continuing debate has concerned the extent to which observed unskilled and unaware effects are due to properties of the measurement or reflect actual relations between skill and awareness. It is recognized that both play a role in the observed unskilled and unaware effects.

However, metacognitive resolution is typically measured with metrics that are asserted to be independent of the participants' performance, skill, or knowledge in the primary task. In an influential article @Nelsoncomparisoncurrentmeasures1984 recommended the Goodman-Kruskal gamma correlation [@GoodmanMeasuresAssociationCross1954] as a measure of resolution, partly because it is theoretically independent of task performance [see also @GonzalezMeasuringordinalassociation1996]. Other measures of resolution include Pearson's *r* [@NelsonNorms300generalinformation1980], the phi correlation [@KornellTransferMetacognitiveSkills2007], and signal detection theoretic measures [@benjamin2008measurement; @HighamNewimprovedgamma2018]. Although computationally different, these metrics measure the trial-by-trial association between response accuracy and metacognitive rating in a way that is usually assumed to quantify metacognitive ability independent of task performance. However, it remains a possibility that metacognitive resolution is empirically related to task performance in a way that would show the unskilled and unaware effect over and beyond its effects on calibration. Such a finding would have dramatic consequences to many areas where metacognitive skills are important, including self-directed studying, to which we turn next.

@@

How important is metacognitive monitoring---resolution---to learning success? One review of 47 experiments found that not only do learners allocate more time to more difficult items, learners' metacognitive judgments negatively predict the amount of time they allocate for studying that item [@SonMetacognitivecontrolstrategies2000]. These results suggest that people are aware of how well they know and use this metacognitive knowledge to guide learning, leading to the hypothesis that students with greater metacognitive resolution may be better learners: Resolution and task performance should be positively correlated across participants. If true, this finding would further support the proposal that metacognitive monitoring is used to control learning behavior, with a positive impact on learning success [@nelson1994investigate]. It would also suggest that unskilled individuals are, indeed, less aware than their more skilled peers.

@@

In Experiment 1, we collated data from six very similar experiments investigating mathematics learning. There were differences between experiments, such as testing medium (computer or paper) and age (middle school or undergraduate), but our focus here was not to investigate these factors' impact on mathematics performance or metacognition. Rather, we used this large dataset to examine the possible relationship between metacognitive resolution and (mathematics) performance, in a multiple-choice testing context. The common procedure was that participants completed mathematics tests consisting of 4-alternative multiple-choice problems, and rated their confidence in the accuracy of each of their answers.

With respect to resolution in mathematics study, two previous studies which contained a resolution measure have reported conflicting results. @SieglerDevelopmentalindividualdifferences2013, in a study of middle school students' fraction arithmetic skills, reported that students' confidence ratings were on average 0.7 points greater for correct than incorrect answers on a 1-5 scale, suggesting that young learners of mathematics have reasonably accurate metacognitions about their answers' accuracy (though the difference in confidence is small). @SchrawEffectGeneralizedMetacognitive1996 tested university undergraduates on probability problems and had them rate their confidence in their answers. The correlation between confidence and accuracy in that study was not statistically significant (Pearson's *r* = -.03)[^1], indicating that university students' metacognitive resolution (within probability calculations) is not accurate. However, neither study addressed the potential correlation between resolution and mathematics performance---the unskilled and unaware phenomenon---which we investigate here.

@@

### Experiment 1A

@@

@@

### Experiment 1B

@@

### Experiment 1C

@@

### Experiment 1D

@@

### Experiment 1E

@@

### Experiment 1F

@@

Participants completed four mathematics tests as part of an online mathematics tutorial. Each test consisted of ten problems, presented on the top of the screen, with the answer alternatives below. Participants chose their preferred response by clicking a box next to it. They then clicked "Submit", and proceeded to the next screen, where they rated their confidence in the accuracy of their response by clicking on a visual analog scale. After indicating their degree of confidence, they clicked "Submit" to proceed to the next screen. The following screen allowed the participant to view different types of instructional videos related to the mathematics problems, but these are not analyzed in the current study. The tests were completed in one 90-minute session, on individual computers, in groups of up to four supervised by an experimenter.

@@

```{r math-dtab, results = 'asis'}
new_names <- tibble(
  key = c("zroc_auc_gamma", "gamma_old", "zroc_da", "phi", "zroc_auc", "trap_auc", "proportion_correct", "mean_rating"),
  Metric = c("Gamma (ROC)", "Gamma (pairs)", "da", "Phi", "AUC (zROC)", "AUC (trap)", "Proportion Correct", "Mean confidence")
)
tab <- math_metrics %>%
  gather(key, value, proportion_correct, zroc_auc_gamma, zroc_da, gamma_old) %>%
  group_by(key, Experiment) %>%
  group_modify(~ data.frame(t(smean.cl.boot(.x$value, B = 1000)))) %>%
  ungroup() %>%
  left_join(new_names) %>%
  right_join(math_subjects) %>%
  mutate_at(vars(Mean, Lower, Upper), ~ format(round(., 2), nsmall = 2)) %>%
  mutate(result = glue("{Mean} [{Lower}, {Upper}]")) %>%
  select(Experiment, N, Metric, result) %>%
  spread(Metric, result) %>%
  select(Experiment, N, `Proportion Correct`, everything())
apa_table(
  tab,
  "Measures of mathematics performance and resolution in Experiment 1. Numbers indicate means with 95\\% CIs in square brackets."
)
```

@@

```{r math-rtab, results = 'asis'}
tab <- math_metrics %>%
  gather(key, value, zroc_da, zroc_auc_gamma, gamma_old) %>%
  left_join(new_names) %>%
  group_by(Experiment, Metric) %>% 
  group_modify(
    ~tidy(cor.test(.x$value, .x$proportion_correct, method = "kendall"))
  ) %>%
  mutate(p.value = pvalue(p.value)) %>%
  mutate(result = format(round(estimate, 2), nsmall = 2, trim = TRUE)) %>%
  mutate(result = glue("{result} ({p.value})")) %>%
  select(Experiment, Metric, result) %>%
  ungroup() %>%
  pivot_wider(names_from = c(Metric), values_from = result)
apa_table(
  tab, 
  caption = "Correlation between mathematics performance and three metrics of metacognitive resolution in Experiment 1."
)
```

@@

```{r trivia-dtab, results = 'asis'}
tmp1 <- trivia_metrics %>% 
  select(
    session, condition, proportion_correct, 
    mean_rating, zroc_da, zroc_auc_gamma
  ) %>% 
  gather(key, value, -session, -condition) %>% 
  spread(condition, value) %>% 
  mutate(difference = `2AFC`-Free) %>% 
  group_by(key) %>% 
  group_modify(~tidy(t.test(.$difference))) %>% 
  # mutate(p.value = pvalue(p.value), parameter = round(parameter, 0)) %>% 
  mutate_if(is.numeric, ~format(round(., 2), nsmall = 2)) %>%
  ungroup() %>% 
  transmute(
    key = key,
    result = glue("{estimate} [{conf.low}, {conf.high}]")
  ) %>% 
  left_join(new_names) %>% 
  select(-key) %>% 
  spread(Metric, result) %>% 
  add_column(condition = "2AFC - Free", .before = 1)
tmp2 <- trivia_metrics %>%
  gather(
    key, 
    value, 
    proportion_correct, mean_rating, zroc_auc_gamma, zroc_da,
  ) %>% 
  group_by(key, condition) %>%
  group_modify(~ data.frame(t(smean.cl.boot(.x$value, B = 1000)))) %>%
  ungroup() %>%
  left_join(new_names) %>%
  mutate_at(vars(Mean, Lower, Upper), ~ format(round(., 2), nsmall = 2)) %>%
  mutate(result = glue("{Mean} [{Lower}, {Upper}]")) %>%
  select(condition, Metric, result) %>%
  spread(Metric, result) %>%
  select(condition, `Proportion Correct`, `Mean confidence`, everything())
bind_rows(tmp2, tmp1) %>% 
  apa_table(
    caption = "Measures of general information test performance and metacognition in Experiment 2. Numbers indicate means with 95\\% CIs in square brackets."
  )
```

@@

```{r trivia-ctab, results = 'asis'}
tmp <- trivia_metrics %>%
  gather(key, value, gamma_old, zroc_da, zroc_auc_gamma) %>%
  left_join(new_names) %>%
  group_by(condition, Metric)
tab <- group_modify(
  tmp,
  ~tidy(cor.test(.x$value, .x$proportion_correct, method = "kendall"))
) %>%
  mutate(p.value = pvalue(p.value)) %>%
  mutate(result = format(round(estimate, 2), nsmall = 2, trim = TRUE)) %>%
  mutate(result = glue("{result} ({p.value})")) %>%
  select(condition, Metric, result) %>%
  ungroup() %>%
  pivot_wider(names_from = c(Metric), values_from = result)
apa_table(
  tab, 
  caption = "Correlation between general information test performance and three metrics of metacognitive resolution in Experiment 2."
  )
```
